Estimating duration in the presence of misclassification

### 2024-01-16 cis-imperfect-testing.tex
Fix small issues

I modified the simulation study from \cref{E-perf-test:sec:simulation-study} to include the possibility of false negatives.
More single positive episodes are seen at lower values of $\psens$, with a value between 60\% and 80\% reproducing the number of single positive episodes observed in the CIS data (see \cref{imperf-test:fig:sim-single-pos}).
In \cref{E-ATACCC}, I estimated that $\psens$ ($1-\rho$ in \cref{E-ATACCC}'s parameterisation) is 95\% (95\% CrI: 96\%--93\%).
The daily testing in the ATACCC study, used for the \cref{E-ATACCC} estimates, means this is a reliable estimate during the period for which the individuals are followed-up.
The requirement for a much lower value of $\psens$ in the simulation study suggests this model of false negatives is inadequate.

@@

This false negative would occur on day $b_i + \tau_{\sched_i}(b_i)$ (see\todo{ref where this was derived}).
A false negative occurring requires that the episode has not yet ended but a negative still occurs.
The episode has not yet ended at the time of the test if $e_i = b_i + d_i - 1$ is after the test, that is $d_i > \tau_{\sched_i}(b_i)$.
Conditional on the episode having not yet ended, the test result is negative with probability $1 - \psens$.

@@

In this section I apply the model described in this chapter to the CIS episodes dataset I described in \cref{E-perf-test:sec:approach}.
This is the infection episodes with start dates between and\todo{check dataset inclusion criteria}.

>>>>

I modified the simulation study from \cref{E-perf-test:sec:simulation-study} to include the possibility of false negatives.
More single positive episodes are seen at lower values of $\psens$, with a value between 60\% and 80\% reproducing the number of single positive episodes observed in the CIS data (see \cref{imperf-test:fig:sim-single-pos}).
In \cref{E-ATACCC}, I estimated that $\psens$ ($1-\rho$ in \cref{E-ATACCC}'s parameterisation) is 95\% (95\% CrI: 93--96\%).
The daily testing in the ATACCC study, used for the \cref{E-ATACCC} estimates, means this is a reliable estimate during the period for which the individuals are followed-up.
The requirement for a much lower value of $\psens$ in the simulation study suggests this model of false negatives is inadequate.

@@

This false negative would occur on day $b_i + \tau_{\sched_i}(b_i)$ (see \cref{E-perf-test:sec:model}).
A false negative occurring requires that the episode has not yet ended but a negative still occurs.
The episode has not yet ended at the time of the test if $e_i = b_i + d_i - 1$ is after the test, that is $d_i > \tau_{\sched_i}(b_i)$.
Conditional on the episode having not yet ended, the test result is negative with probability $1 - \psens$.

@@

In this section I apply the model described in this chapter to the CIS episodes dataset I described in \cref{E-perf-test:sec:approach}.
This is the 4,800 infection episodes that were first detected between 10th Oct 2020 and 6th Dec 2020 inclusive, with negatives bounding the start and end time of the episode.
